High-accuracy neutron diffusion calculations based on integral transport theory

### 2019-12-12 docs/EPJP2019/Gross-EPJP-2019.tex
latest modification and production of marked copy

The Ronen algorithm used to solve the critical eigenvalue problem in the slab is described as follows (see Fig.~\ref{fig:RM-algo}):
\begin{enumerate}
	\item{\sl Initialize}\label{it:init} The algorithm receives the geometry and the cross sections (XS) of the problem as input data. At this stage, the correction factors $\delta D^{(0)}$ are set to zero and the initial pure-diffusion operator is constructed, that is $\mathcal{A}^{(0)} = \mathcal{A}_0$. Initial guesses for the flux $\phi^{(0)}$ and the multiplication factor $k_\textrm{eff}^{(0)}$ are set.
	\item{\sl Diffusion solver}\label{it:DF-solve} A one-dimensional multigroup diffusion solver is executed with the migration operator $\mathcal{A}^{(k)} = \mathcal{A}_0 + \delta A^{(k)}$ to determine new estimates of the flux $\phi^{(k)}$ and of the multiplication factor $k_\textrm{eff}^{(k)}$.
	\item{\sl Convergence check}\label{it:cvg} Convergence is checked with the relative residuals on the flux and on the multiplication factor between iteration $k$ and $(k-1)$; Ronen iterations are stopped if the relative residuals fall within the input tolerances.
	\item{\sl Estimate currents}\label{it:Js} Both the diffusion current $\jd^{(k)}$ (Eq.~\ref{eq:JD}) and the transport current $\jtrr^{(k)}$ (Eq.~\ref{eq:tot-J}) are calculated using $\phi^{(k)}$ and $k_\textrm{eff}^{(k)}$.
	\item{\sl Update correction}\label{it:dD} The correction factors $\delta D^{(k+1)}$ are obtained using $\delj^{(k)}$ and Eq.~\eqref{eq:dJ} in order to update the migration operator $\mathcal{A}^{(k+1)} = \mathcal{A}_0+\delta \mathcal{A}^{(k+1)}$ (Eq.~\ref{eq:FD_diff_org}), and continue with step~\ref{it:DF-solve}.
\end{enumerate}

>>>>

The Ronen algorithm used to solve the critical eigenvalue problem in the slab is described as follows (see Fig.~\ref{fig:RM-algo}):
\begin{enumerate}
	\item{\sl Initialize}\label{it:init} - The algorithm receives the geometry and the cross sections (XS) of the problem as input data. At this stage, the correction factors $\delta D^{(0)}$ are set to zero and the initial pure-diffusion operator is constructed, that is $\mathcal{A}^{(0)} = \mathcal{A}_0$. Initial guesses for the flux $\phi^{(0)}$ and the multiplication factor $k_\textrm{eff}^{(0)}$ are set.
	\item{\sl Diffusion solver}\label{it:DF-solve} - A one-dimensional multigroup diffusion solver is executed with the migration operator $\mathcal{A}^{(k)} = \mathcal{A}_0 + \delta A^{(k)}$ to determine new estimates of the flux $\phi^{(k)}$ and of the multiplication factor $k_\textrm{eff}^{(k)}$.
	\item{\sl Convergence check}\label{it:cvg} - Convergence is checked with the relative residuals on the flux and on the multiplication factor between iteration $k$ and $(k-1)$; Ronen iterations are stopped if the relative residuals fall within the input tolerances.
	\item{\sl Estimate currents}\label{it:Js} - Both the diffusion current $\jd^{(k)}$ (Eq.~\ref{eq:JD}) and the transport current $\jtrr^{(k)}$ (Eq.~\ref{eq:tot-J}) are calculated using $\phi^{(k)}$ and $k_\textrm{eff}^{(k)}$.
	\item{\sl Update correction}\label{it:dD} - The correction factors $\delta D^{(k+1)}$ are obtained using $\delj^{(k)}$ and Eq.~\eqref{eq:dJ} in order to update the migration operator $\mathcal{A}^{(k+1)} = \mathcal{A}_0+\delta \mathcal{A}^{(k+1)}$ (Eq.~\ref{eq:FD_diff_org}), and continue with step~\ref{it:DF-solve}.
\end{enumerate}
